---
title: "RO-Wave Energy"
author: "Hattie"
date: "6/2/2020"
output: pdf_document
---

```{r}
library("tidymodels")
library("tidyverse"); theme_set(theme_minimal())
theme_update(panel.grid.minor = element_blank())
library("lubridate")
library("ggplot2")
library("gridExtra")
library("viridis")
```

```{r}
load('../data/data.Rdata')

N <- 9
OUTPUT <- FALSE

str(data)
head(data)
colnames(data)
view(data)

## experiments summary
data %>%
  select(-time, -runtime_h, -system_mode) %>%
  group_by(experiment) %>%
  summarise_all(mean) %>%
  as.data.frame

## feed pressure distribution by experiment
ggplot(data, aes(x = feed_pressure_psi, color = experiment)) +
  geom_density() +
  ggtitle('Feed Pressure Distribution') +
  labs(subtitle = 'by experiment', color = 'Exp.') +
  xlab('Feed Pressure (psi)') + ylab('Density') +
  theme_minimal()

## plots of conductivity for each experiment.
for (i in 1:N) {
  df <- gather(data, key = measure, value = value,
               c('permeate_conductivity_high_us', 'permeate_conductivity_low_us'))
  if (OUTPUT) {
    pdf(file = paste('../plots/permeate_conductivity/permeate_conductivity', i,
                     '.pdf', sep = ''), height = 4.0, width = 8.67)
  }
  g <- df %>%
    filter(experiment == i) %>%
    ggplot(aes(time, value, group = measure, color = measure)) +
    geom_line() +
    ggtitle('Permeate Conductivity') +
    labs(subtitle = paste('Experiment', i), color = 'Measure') +
    xlab('Time') + ylab('Permeate Conductivity') + ylim(0, 1000) +
    scale_color_manual(values = c('SteelBlue', 'Orange3'),
                       labels = c('High', 'Low')) +
    theme_minimal()
  print(g)
  if (OUTPUT) {
    dev.off()
  }
}
rm(df, g)

## Plots of feed pressure for each experiment.
for (i in 1:N) {
  if (OUTPUT) {
    pdf(file = paste('../plots/feed_pressure/feed_pressure', i,
                     '.pdf', sep = ''), height = 4.0, width = 8.67)
  }
  g <- data %>%
    filter(experiment == i) %>%
    ggplot(aes(time, feed_pressure_psi)) +
    geom_line(size = 0.25) +
    ggtitle('Feed Pressure') +
    labs(subtitle = paste('Experiment', i)) +
    xlab('Time') + ylab('Feed Pressure (psi)') + ylim(-5.61, 1114.9) +
    theme_minimal()
  print(g)
  if (OUTPUT) {
    dev.off()
  }
}

## Plots of feed flowrate for each experiment.
for (i in 1:N) {
  if (OUTPUT) {
    pdf(file = paste('../plots/feed_flowrate/feed_flowrate', i,
                     '.pdf', sep = ''), height = 4.0, width = 8.67)
  }
  g <- data %>%
    filter(experiment == i) %>%
    ggplot(aes(time, feed_flowrate_l_min)) +
    geom_line(size = 0.25) +
    ggtitle('Feed Flowrate') +
    labs(subtitle = paste('Experiment', i)) +
    xlab('Time') + ylab('Feed Flowrate') +
    theme_minimal()
  print(g)
  if (OUTPUT) {
    dev.off()
  }
}

## Plots of water flux for each experiment.
for (i in 1:N) {
  pdf(file = paste('../plots/ts/water_flux/water_flux', i,
                   '.pdf', sep = ''), height = 4.0, width = 8.67)
  g <- data %>%
    filter(experiment == i) %>%
    ggplot(aes(time, water_flux_lmh)) +
    geom_line(size = 0.25) +
    ggtitle('Water Flux') +
    labs(subtitle = paste('Experiment', i)) +
    xlab('Time') + ylab('Water Flux (lmh)') +
    theme_minimal()
  print(g)
  dev.off()
}

## Scatterplot matrices.
colors <- plasma(9)
for (i in 1:N) {
  pdf(file = paste('../plots/scatter_matrix/scatter_matrix', i,
                   '.pdf', sep = ''), height = 5.0, width = 5.0)
  data %>%
    filter(experiment == i) %>%
    select(feed_pressure_psi, feed_flowrate_l_min,
           feed_pump_power_pct, water_flux_lmh) %>%
    pairs(col = colors[i], cex = 0.20)
  dev.off()
}
```
  

```{r}
data %>% 
  ggplot(aes(x = water_flux_lmh, y = time, color = factor(experiment))) + 
  geom_line() +
  facet_wrap(experiment~.)
```

```{r}

## Feed Pump Power Over Time
for (i in 1:N) {
  g <- data %>%
    filter(experiment == i) %>%
    ggplot(aes(time, feed_pump_power_pct)) +
    geom_line(size = 0.25) +
    ggtitle('Feed Pump Power') +
    labs(subtitle = paste('Experiment', i)) +
    xlab('Time') + ylab('Feed Pump Power') +
    theme_minimal()
  print(g)
}

## Permeate Conductivity Over Time
for (i in 1:N) {
  g <- data %>%
    filter(experiment == i) %>%
    ggplot(aes(time, permeate_conductivity_high_us)) +
    geom_line(size = 0.25) +
    ggtitle('Perm (High) Conductivity') +
    labs(subtitle = paste('Experiment', i)) +
    xlab('Time') + ylab('Permeate Conductivity') +
    theme_minimal()
  print(g)
}

## Permeate Flow Rate
for (i in 1:N) {
  g <- data %>%
    filter(experiment == i) %>%
    ggplot(aes(time, permeate_flowrate_l_min)) +
    geom_line(size = 0.25) +
    ggtitle('Permeate Flow Rate') +
    labs(subtitle = paste('Experiment', i)) +
    xlab('Time') + ylab('Permeate Flow Rate') +
    theme_minimal()
  print(g)
}

## Feed Flow Rate
for (i in 1:N) {
  g <- data %>%
    filter(experiment == i) %>%
    ggplot(aes(time, feed_flowrate_l_min)) +
    geom_line(size = 0.25) +
    ggtitle('Feed Flow Rate') +
    labs(subtitle = paste('Experiment', i)) +
    xlab('Time') + ylab('Feed Flow Rate') +
    theme_minimal()
  print(g)
}

## Feed Pressure
for (i in 1:N) {
  g <- data %>%
    filter(experiment == i) %>%
    ggplot(aes(time, feed_pressure_psi)) +
    geom_line(size = 0.25) +
    ggtitle('Feed Flow Rate') +
    labs(subtitle = paste('Experiment', i)) +
    xlab('Time') + ylab('Feed Pressure') +
    theme_minimal()
  print(g)
}

## To See How Water Flux Changes as Pump Power Increases
for (i in 1:N) {
  g <- data %>%
    filter(experiment == i) %>%
    ggplot(aes(feed_pump_power_pct, water_flux_lmh)) +
    geom_line(size = 0.25) +
    ggtitle('Water Flux by Pump Power') +
    labs(subtitle = paste('Experiment', i)) +
    xlab('Pump Power') + ylab('Water Flux') +
    theme_minimal()
  print(g)
}

## To See How Conductivity Changes as Pump Power Increases
for (i in 1:N) {
  g <- data %>%
    filter(experiment == i) %>%
    ggplot(aes(feed_pump_power_pct, permeate_conductivity_high_us)) +
    geom_line() +
    ggtitle('Conductivity by Pump Power') +
    labs(subtitle = paste('Experiment', i)) +
    xlab('Pump Power') + ylab('Conductivity') +
    theme_minimal()
  print(g)
}

for (i in 1:N) {
  g <- data %>%
    filter(experiment == i) %>%
    ggplot(aes(time, water_flux_lmh)) +
    geom_line(size = 0.25) +
    ggtitle('Water Flux') +
    labs(subtitle = paste('Experiment', i)) +
    xlab('Time') + ylab('Water Flux') +
    theme_minimal()
  print(g)
}
```



```{r}
ex1Data <- data %>% 
  filter(experiment == 1)

ex2Data <- data %>% 
  filter(experiment == 2)
ts.plot(ex2Data$water_flux_lmh)

ex3data <- data %>% 
  filter(experiment == 3) 

feed_pressure3 <- ex3data %>% 
  ggplot(aes(time, feed_pressure_psi)) + 
  geom_line()
water_flux3 <- ex3data %>% 
  ggplot(aes(time, water_flux_lmh)) + 
  geom_line()
flowrate3 <- ex3data %>% 
  ggplot(aes(time, feed_flowrate_l_min)) + 
  geom_line()
conductivity3 <- ex3data %>% 
  ggplot(aes(time, permeate_conductivity_high_us)) + 
  geom_line()

feed_pressure3
water_flux3
flowrate3
conductivity3

ex4Data <- data %>% 
  filter(experiment == 4)
#view(ex4Data)
ts.plot(ex4Data$water_flux_lmh)

ex5Data <- data %>% 
  filter(experiment == 5)
#view(ex5Data)
ts.plot(ex5Data$water_flux_lmh)

ex7Data <- data %>% 
  filter(experiment == 7)
#view(ex7Data)
ts.plot(ex7Data$water_flux_lmh)

ex8Data <- data %>% 
  filter(experiment == 8)
#view(ex8Data)
ts.plot(ex8Data$water_flux_lmh)

ex9Data <- data %>% 
  filter(experiment == 9)
#view(ex9Data)
ts.plot(ex9Data$water_flux_lmh)

exTenData <- data %>% 
  filter(experiment == 10)
#view(ex10Data)
ts.plot(exTenData$water_flux_lmh)

```

DONE: 
## taking out repetative data
data <- subset(data, data$experiment != 6 & data$experiment != 11)
unique(data$experiment)
view(data)
## convert date, time to time: POSIXct
data$time <- paste(data$date, data$time) %>%
  parse_date_time('%Y-%m-%d %H:%M:%S %p')

data <- data %>%
  select(-date)
data$experiment <- as.factor(data$experiment)
rm(temp)

## divide data by experiment
tapply(data$experiment, data$experiment, length)

data %>% 
  ggplot(data, ase)

data %>%
  filter(experiment == 2 | experiment == 11) %>%
  select(-time, -permeate_tank_level, -feed_cleaning_valve_state,
         -permeate_discharge_valve_state, -system_mode) %>%
  group_by(experiment) %>%
  summarise_all(mean) %>%
  as.data.frame

data %>%
  filter(experiment == 1 | experiment == 6) %>%
  select(-time, -permeate_tank_level, -feed_cleaning_valve_state,
         -permeate_discharge_valve_state, -system_mode) %>%
  group_by(experiment) %>%
  summarise_all(mean) %>%
  as.data.frame






